Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-03 Draft/Draft.Rmd
some edits

Indirect interactions are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. Motifs are commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002]. The work of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

Linking the structural porperties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, motifs are abstract representations often decoupled from species ecology. Remarkably, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021]. Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014]. Hence, exploring how the main species reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1. Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks", fig.width=10,fig.height=8}
library(tidyverse)
library(RColorBrewer)
source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")

@@

1) over and under represented motifs
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=percentil_sizeclass, 
                 color = as.factor(Broad_categories)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                size=2)+
  labs(y="Motif", x = "Percentile",colour="Motif classification")+
  theme_bw()

>>>>

Indirect interactions (i.e., motifs) commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002] are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

Linking the structural porperties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, motifs are abstract representations often decoupled from species ecology. Remarkably, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021]. Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014]. Hence, exploring how the main reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 1. Adapted figure of Simmons et al., 2019 with all the possible motifs from two to five species in bipartite networks. There is a total of 17 possible motifs with 46 different positions denoted within each node.", fig.width=10,fig.height=8}
library(tidyverse)
library(RColorBrewer)
source("../Scripts/Scripts_Alfonso/plot_motif_positionsV2.R")

@@

1) over and under represented motifs
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="Figure 2. Comparison of the motif frequencies between empirical and simulated networks. Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks. The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=8,fig.height=5}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=percentil_sizeclass, 
                 color = as.factor(Broad_categories)),
             position = "jitter",alpha=0.55)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                size=2)+
  labs(y="Motif", x = "Percentile",colour="Path length classification")+
  theme_bw() + scale_color_manual(labels = c('Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")),
    'Strong' = expression(paste("Complete (", bar(x), " = 1.38)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("deepskyblue3","maroon","darkgoldenrod2","grey25")) +
theme(legend.text.align = 0)
